Chemically Selective Transport in a Cross-Linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-06-25 Ben_Manuscripts/transport/Final_Draft.tex
Added one more citation for TIP3P justification

  We simulated water molecules using the TIP3P water model because it is the
  water model that GAFF and other AMBER family parameters have been optimized
  with.~\cite{florova_explicit_2010}

>>>>

  We simulated water molecules using the TIP3P water model because it is the
  water model that GAFF and other AMBER family parameters have been optimized
  with.~\cite{florova_explicit_2010,ponder_force_2003}
